---
title: Introduction to Katie Li-Hsuan CHANG's HOMEWORK1016
author: Katie Li-Hsuan CHANG
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is the homework of Katie Li-Hsuan CHANG for the R course due on 16 October 2017.
```{r}
library(HOMEWORK1016)
```


The function draw_a_name gives you the overview of how many people were using the name you want to look up:
```{r}
draw_a_name("Katie","F")
```

The function draw_names does similar thing with the function draw_a_name, while you can input 2 names at once:
```{r}
draw_names(c("Beatriz","John"))
```

The function save_as_csv saves a csv file to the designated folder you assigned:
```{r}
save_as_csv(iris, "/Users/katiechang/Desktop/test3.csv")
```

The function my_csv_reader reads all the csv files from the designated folder and returns the file names:
```{r}
my_csv_reader ("../..")
```

The function multi_excel takes an excel file and reads through all the sheets inside:
```{r}
multi_excel ("/Users/katiechang/Desktop/Ecole Polytechnique 2017 2018/R Python/Day2 03 October 2017/TD 3/jeux.xlsx")
```

